Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
plots

\documentclass[11pt,twocolumn]{article} 
\usepackage{simpleConference}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}

@@

\section{Results}
We found that utilizing information from the gold segmentations, we were able to substantially increase our
performance, from an accuracy of 65.5\% to 81.7\% with English, and from 47.9\% to 69.7\% with Turkish.
This is a substantial but expected increase; observing the unsupervised model reveals that it performs
many segmentations with nonexistent affixes, which are rectified by providing input about known affixes.

>>>>

\documentclass[11pt,twocolumn]{article} 
\usepackage{simpleConference}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}
\usepackage{tikz,pgfplots}

\newcommand\engsmallw{2514}
\newcommand\engmedw{48146}
\newcommand\englargew{126537}
\newcommand\engfullw{878036}
\newcommand\tursmallw{1592}
\newcommand\turmedw{14909}
\newcommand\turlargew{89023}
\newcommand\turfullw{617298}

\newcommand\engsmallv{10000}
\newcommand\engmedv{100000}
\newcommand\englargev{500000}
\newcommand\engfullv{1477761}
\newcommand\tursmallv{10000}
\newcommand\turmedv{100000}
\newcommand\turlargev{300000}
\newcommand\turfullv{593836}

@@

\section{Results}
\begin{figure}
    \begin{tikzpicture}
        \begin{axis}[
                height=0.8\linewidth,
                width=\linewidth,
                xmin=1000, xmax=300000,
                ymin=0, ymax=1,
                xmode=log,
                xlabel=Training Vocab Size,
                ylabel=F-1 Score,
            ]
            \addplot coordinates {
                (\engsmallw, 0.556)
                (\engmedw, 0.656)
                (\englargew, 0.383)
            };
            \addlegendentry{English}
            \addplot coordinates {
                (\tursmallw, 0.124)
                (\turmedw, 0.479)
                (\turlargew, 0.520)
            };
            \addlegendentry{Turkish}
        \end{axis}
    \end{tikzpicture}
    \label{fig:unsupervised}
    \caption{Performance of unsupervised model after frequency thresholding training data}
\end{figure}

\begin{figure}
    \begin{tikzpicture}
        \begin{axis}[
                height=0.8\linewidth,
                width=\linewidth,
                xmin=0, xmax=20,
                ymin=0, ymax=1,
                xlabel=$\alpha$,
                ylabel=F-1 Score,
                legend pos=south east,
            ]
            \addplot coordinates {
                (0, 0.656)
                (0.1, 0.683)
                (1, 0.752)
                (3, 0.803)
                (5, 0.815)
                (8, 0.824)
                (10, 0.823)
                (12, 0.821)
                (15, 0.822)
                (20, 0.817)
            };
            \addlegendentry{English}
            \addplot coordinates {
                (0, 0.479)
                (0.1, 0.580)
                (1, 0.663)
                (3, 0.668)
                (5, 0.670)
                (8, 0.680)
                (10, 0.680)
                (20, 0.691)
                (50, 0.697)
            };
            \addlegendentry{Turkish}
        \end{axis}
    \end{tikzpicture}
    \label{fig:supervised}
    \caption{Performance of semi-supervised model based on $\alpha$.}
\end{figure}

We found that utilizing information from the gold segmentations, we were able to substantially increase our
performance, from an accuracy of 65.5\% to 81.7\% with English, and from 47.9\% to 69.7\% with Turkish.
This is a substantial but expected increase; observing the unsupervised model reveals that it performs
many segmentations with nonexistent affixes, which are rectified by providing input about known affixes.
